### 2020-06-01 5_evaluation.tex
Add section on predicting strong scalability.

>>>>

\input{e9_strong}

{\color{blue}
\subsection{Predicting Strong Scaling with METG}

% Summary:

% Charm++:
% Limit/Ideal intersects at: 55 nodes, 0.068 s
% Limit/Actual intersects at: 67 nodes, 0.086 s
% Limit/Ideal vs Limit/Actual gap in nodes: 1.22x
% Limit/Ideal vs Limit/Actual gap in time: 1.27x

% Overall (out of 11 systems that perform well enough to have an intersection):
% Limit/Ideal vs Limit/Actual gap in nodes:
%   mean: 1.61x
%   median: 1.60x
%   min: 1.13x
%   max: 2.19x
% Limit/Ideal vs Limit/Actual gap in time:
%   mean: 1.28x
%   median: 1.27x
%   min: 1.01x
%   max: 1.69x

We can use METG to predict the scalability of a code. Figure
\ref{fig:strong-scaling} shows a strong scaling execution of Task
Bench stencil. Lines marked ``actual'' represent strong scaling
measurements, while ones marked ``limit'' are computed by multiplying
METG(50\%) by tasks per core (in this case, 1000). Intuitively,
``limit'' is the smallest time to solution that could be achieved for
\emph{any} problem size at that node count, while maintaining 50\%
efficiency. Note that ``actual'' eventually falls below ``limit''
because ``actual'' is not constrained to 50\% efficiency and
eventually drops below this level.

There are two points of intest on each ``limit'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked in
Figure~\ref{fig:strong-scaling} with a black square and a black
circle, respectively. Notably, the intersection between ideal and
``limit'' requires only a single node run, along with measurements of
METG(50\%) at each node count. Using this data it is possible to
predict the strong scalability of the code: i.e., the smallest time to
solution, and the number of nodes at which that time to solution is
achieved, while maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling} this can be seen as the distance
between the black square and circle, which differ by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.

When we compute this same measure across all of the 11 programming
systems that scale well enough to perform the experiment, we find that
the average separation between the ideal and actual intersection
points is $1.61\times$ in node count (max $2.19\times$, min
$1.13\times$) and $1.28\times$ in time to solution (max $1.69x$, min
$1.01\times$).

} % color
